
\documentclass[letterpaper]{article}
    \usepackage{fullpage}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{multicol}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}


% DEFINITIONS FOR RESUME %
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{12pt} \large\textsc{#1}}
    \vspace*{-12pt} \lineunder
}

% START DOCUMENT HERE %

\begin{document}
\vspace*{-25pt}
    

%==== Heading ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape \textbf {Maverick Reynolds}}\\
	mcreynolds02@gmail.com $\cdot$ 954.224.6019\\
\end{center}


%==== Education ====%
\header{Education}
\textbf{University of Central Florida}\hfill Orlando, FL\\
B.S. Computational Mathematics \hfill Expected Graduation: May 2025\\
\hspace{7mm} \textit{GPA: 3.8}\\
\vspace{3mm}


%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{UCF Crimes} \hfill Feb 2023 - Present \\
\textit{Python, SQL, OpenAI, Pandas} \hfill \textit{ucf-crimes.streamlit.app}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Parsed over 300 total incident reports from UCF Police Department's public daily log into SQL database.
	\item Used regex and Levenshtein distance with Python to preprocess addresses before geocoding.
	\item Created images using Google Places API for distribution with Discord and Instagram.
	\item Incorporated PandasAI to allow user to ask questions about the database using natural language processing.
	\item Generated embeddings for each incident using OpenAI's Embeddings API to help improve title search accuracy.
\end{itemize}

\textbf{Multidimensional Cross Correlation} \hfill Jun 2023 - Jul 2023 \\
\textit{Python, Streamlit, SciPy} \hfill \textit{adjusted-cross-correlation.streamlit.app}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed algorithm using SciPy to measure and detect shifts in 2-dimensional quantitative data (>1000 entries each) along a single axis.
	\item Deployed web-applet using Streamlit to allow interactive use with data collected during electrochemical research conducted at Florida Tech.
\end{itemize}

\textbf{IEEE Phantom Arm Project} \hfill Sep 2022 - Nov 2022\\
\textit{C, GNU Scientific Library} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Calculated distances necessary to extend actuators on 3DoF Stewart platform to imitate human neck (ball-and-socket) rotation.
	\item Wrote software using C libraries for matrix addition and multiplication.
\end{itemize}

\textbf{Word Ladder Project} \hfill Jan 2022 - Feb 2022\\
\textit{Python, DFS} \hfill \textit{github.com/mavreyn/word-ladder}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Scripted algorithm to determine shortest path from one string to another while changing one letter each step. (e.g. "cat" to "car" to "bar")
	\item Performed recursive tree traversal using depth-first searching techniques to determine if the target word is a child of the current subtree.
    \item Used nodes from the valid scrabble dictionary (>170,000 words) to generate path.
\end{itemize}

\vspace{2mm}


%==== Skills and Abilities ====%
\header{Skills \& Abilities}
\begin{multicols}{2}
    \begin{itemize} \itemsep 1pt
        \item RESTful APIs
        \item LaTeX Typesetting
        \item Advanced Python
        \item Basic Database Management
        \item Prompt Engineering, NLP
        \item Web-applet Development
        \item Customer Service (Publix, Chipotle)
        \item Teamwork
        \item Microsoft Office
        \item Knight Hacks
        \item UCF Astronomy Society: Treasurer, Volunteer
        \item Mu Alpha Theta Honor Society
    \end{itemize}
\end{multicols}

\vspace{2mm}

%==== Awards ====%
\header{Awards}

\textbf{UCF College of Sciences Dean's List} \hfill UCF College of Sciences\\
In recognition of outstanding scholastic achievement for fall 2022 semester \hfill Nov 2022\\
\vspace*{2mm}

\textbf{Florida Academic Scholarship} \hfill Florida Dep. of Ed.\\
For demonstrating academic achievement during high school\hfill May 2021\\
\end{document}

