\documentclass[letterpaper]{article}
    \usepackage{fullpage}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}


% DEFINITIONS FOR RESUME %
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{12pt} \large\textsc{#1}}
    \vspace*{-12pt} \lineunder
}

% START DOCUMENT HERE %

\begin{document}
\vspace*{-25pt}
    

%==== Heading ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape \textbf {Maverick Reynolds}}\\
	Orlando, FL $\cdot$ mcreynolds02@gmail.com $\cdot$ 954.224.6019\\
\end{center}


%==== Smmary ====%
\header{Profile}
\vspace{1mm}
Hardworking third-year UCF student pursuing a degree in computational mathematics. Eager to keep busy and meaningfully contribute while continuing to study throughout the summer term.\\
\vspace{3mm}


%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{UCF First Year Experience} \hfill Orlando, FL\\
\textit{Orientation Assistant} \hfill Jan 2022 - Aug 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Learned about principles of effective teamwork during semester-long leadership program.
	\item Welcomed over 18,000 new students to the University of Central Florida throughout the semester.
	\item Spoke in front of over 750 people during largest and most demanding sessions.
	\item Directed foot traffic during resource fairs and led campus tours for students and their guardians.
	\item Provided constructive program feedback by improving and reordering information in main slideshow presented daily.
\end{itemize}

\textbf{Chipotle Mexican Grill} \hfill Coral Springs, FL\\
\textit{Cashier} \hfill Jun 2021 - Aug 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Served over 200 customers each shift at the establishment's busiest hours.
	\item Restocked lobby materials and cleaned dining room during momentary line breaks.
	\item Resolved daily register failures while maintaining throughput by using register in takeout line when necessary.
	\item Delivered attentive customer service while maintaining composition with more difficult customers.
\end{itemize}
\vspace{1mm}


%==== Skills ====%
\header{Skills}
\vspace{1mm}
\begin{tabular}{ l l }
	Interpersonal: & Problem-solving, quick learner, critical-thinker              \\
	Technical:     & Microsoft Office Suite, LaTeX typesetting, mental math        \\
	Programming:   & Advanced Python, basic C, basic Java                          \\
\end{tabular}
\vspace{3mm}


%==== Involvement ====%
\header{Involvement}

{\textbf{AI@UCF}} {\sl PyTorch, NumPy, Pandas, wandb} \hfill https://ucfai.org\\
\begin{itemize}[topsep=0pt] \itemsep 1pt
    \item Developing prototype AI model designed to recommend various types of media to a user.
    \item Using matrix factorization to determine embeddings from given data set and k-nearest neighbors algorithm to estimate interests of new users.\\
\end{itemize}
\vspace*{2mm}

{\textbf{UCF Astronomy Society}}\hfill https://planets.ucf.edu/astroclub\\
\begin{itemize}[topsep=0pt] \itemsep 1pt
    \item Set up 7 inch Cassegrain telescopes during public Knight Under the Stars stargazing events.
    \item Help visitors locate and learn about well-known objects in the night sky.\\
\end{itemize}
\vspace*{2mm}

{\textbf{IEEE Phantom Arm}} {\sl NumPy, PyBullet} \\
\begin{itemize}[topsep=0pt] \itemsep 1pt
    \item Solving mathematics for forward and inverse kinematics used to control an electromechanical arm.
    \item Creating custom equations based on CAD designs established by hardware and modeling teams.\\
\end{itemize}
\vspace{3mm}


%==== Education ====%
\header{Education}
\textbf{University of Central Florida}\hfill Orlando, FL\\
B.S. Computational Mathematics \hfill Expected Graduation: May 2025\\
\hspace{7mm} \textit{GPA: 3.8}\\
\vspace{3mm}


%==== Awards ====%
\header{Awards}

\textbf{UCF College of Sciences Dean's List} \hfill UCF College of Sciences\\
In recognition of outstanding scholastic achievement for fall 2022 semester \hfill Nov 2022\\
\vspace*{2mm}

\textbf{Florida Academic Scholarship} \hfill Florida Student Financial Aid\\
For demonstrating academic achievement during high school\hfill May 2021\\
\end{document}